PANCHANGE_data_preprocessing

### 2020-08-04 PANCHANGE_data_preprocessing2020-07-15.Rmd
Added OCI-R dataframes to the tibble data frame list.

glad data frame list
```{r glad data frame list}
glad.dfs.list <- list(
  glad.dem.raw.id,
  glad.gad.raw.id,
  glad.mhq.raw.categories,
#  glad.ocir.raw.id,
  glad.pcl.raw.id,
  glad.phq.raw.id,
  coping.glad.gad.raw.id,
  coping.glad.pcl.raw.id,
  coping.glad.phq.raw.id
)
```

>>>>

glad data frame list
```{r glad data frame list}
glad.dfs.list <- list(
  glad.dem.raw.id,
  glad.gad.raw.id,
  glad.mhq.raw.categories,
  glad.ocir.raw.id,
  glad.pcl.raw.id,
  glad.phq.raw.id,
  coping.glad.gad.raw.id,
  coping.glad.pcl.raw.id,
  coping.glad.phq.raw.id,
  coping.glad.ocir.raw.id
)
```
